High-order dynamic neural correlations reflect naturalistic processing in humans

### 2019-04-22 paper/main.tex
WIP paper

\subsubsection*{Generating synthetic data}
Ramping dataset and block dataset. Add details (Fig.~\ref{fig:synthetic_data})
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
  \caption{\textbf{Dynamic correlation recovery with synthetic data.
      a.Recovery using a constant dataset.} Using constant dataset,
    how well can we recover using different
    kernels. \textbf{b. Recovery using random dataset.}
    \textbf{c. Ramping recovery.}  \textbf{d. Block recovery} blah}
  \label{fig:synthetic_data}
\end{figure}

@@

To explore recovery of a constant correlation, we generated syntheic
data sampled from a constant covariance matrix. To do this, we created a random
correlation matrix $K$ of size $s$, and and added a small amount of Gaussian noise
to create a timeseries of for $s$ subjects.     \sim\mthcal{N}(\mu,\,\sigma^{2})

We applied timecorr with a given kernel Fig.~\ref{fig:weights}) to
synthetic data, then correlate each recovered
correlation matrix with the ground truth.  Explore how recovery varies
with the kernel, kernel parameters, and specific structure of the data
(e.g. slow changes as in the ramping dataset, versus rapid changes as
in the block dataset).

>>>>

\subsubsection*{Generating synthetic data}
To explore recovery of a constant covariance (Fig.~\ref{fig:synthetic_data},  A.), we generated syntheic
data sampled from a constant covariance matrix. To do this, we created one random
covariance matrix, $K$, with 50 features, and for each of the 300 timepoints  we
sampled from a Gaussian distribution centered on $K$.  Similarly, we generated synthetic data
sampled from a random covariance matrix (Fig.~\ref{fig:synthetic_data},  B.) by creating a new random
covariance matrix $K(t)$, for each of the 300 timepoints and sampled from a
Gaussian distribution centered on $K(t)$.

To generate synthetic data from a dynamically changing covariance
matrix (ramping covariance matrix Fig.~\ref{fig:synthetic_data},  C.),
we generated two random covariance
matrices, $K_{1}$ and $K_{2}$.  We then computed a covariance matrix
for each of the 300 timepoint, $K(t)$ 
by taking the linearly spaced weights ($w$) of the two random matrices, 
\begin{align}
K(t) = w(t) * K_{1} + 1 - w(t) *  K_{2}
\end{align}

(Fig.~\ref{fig:synthetic_data})

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
  \caption{\textbf{Dynamic correlation recovery with synthetic data.
      a.Recovery using a constant dataset.} Using constant dataset,
    how well can we recover using different
    kernels. \textbf{b. Recovery using random dataset.}
    \textbf{c. Ramping recovery.}  \textbf{d. Block recovery} blah}
  \label{fig:synthetic_data}
\end{figure}

@@

We applied timecorr, using delta and gaussian kernels
Fig.~\ref{fig:weights}) to each of these 
synthetic datasets, then correlate each recovered
correlation matrix with the ground truth.  Explore how recovery varies
with the kernel and the specific structure of the data
(e.g. slow changes as in the ramping dataset, versus rapid changes as
in the block dataset).
